\section{Nebulas Account Address Design}

\subsection{Address Checksum}

Similar to Bitcoin and Ethereum, Nebulas also adopts elliptic curve algorithm as its basic encryption algorithm for Nebulas accounts. A user’s private key is a randomly generated 256-bit binary number, based on which a 64-byte public key can be generated via elliptic curve multiplication. Bitcoin and Ethereum addresses are computed by public key via the deterministic Hash algorithm, and the difference between them lies in: Bitcoin address has the checksum design aiming to prevent a user from sending Bitcoins to a wrong user account accidentally due to entry of several incorrect characters; while Ethereum doesn’t have such checksum design.

%类似于比特币和以太坊，星云链的帐号也是由椭圆曲线算法作为其基础加密算法。用户的私钥是随机生成的256位二进制数，通过椭圆曲线乘法生成64字节的公钥。比特币和以太坊的地址都是由公钥通过确定性的哈希算法运算得到，不同的是：比特币地址有校验码设计，防止用户输错了几个字符而把比特币误发给其它用户，以太坊却没有校验码设计。
We believe that checksum design is reasonable from the perspective of users, so Nebulas address also includes checksum, for which the specific calculation method is provided as follows:

%我们认为从用户的角度看，校验码的设计是合理的，因此星云链的地址也包含了校验码，具体计算方法如下：

\begin{verbatim}
  Data = sha3_256(Public Key)[-20:]
  CheckSum = sha3_256(Data)[0:4]
  Address = "0x" + Hex(Data + CheckSum)
\end{verbatim}

The last 20 bytes of SHA3-256 digest of a public key serve as the major component of an address, for which another SHA3-256 digest should be conducted and the first 4 bytes should be used as a checksum, which is equivalent to the practice of adding a 4-byte checksum to the end of an Ethereum address. For example:

%公钥的SHA3-256摘要的后20位字节作为地址的主要组成部分，对其再做一次SHA3-256摘要，取前4位字节做校验码，其相当于在以太坊的地址尾部加上4字节的校验码。

\begin{enumerate}
  \item  The standard address of Alice’s Ethereum wallet is 0xdf4d22611412132d3e9bd322f82e2940674ec1bc;
  \item  The final address of Nebulas Wallet should be: \\ 0xdf4d22611412132d3e9bd322f82e2940674ec1bc\textbf{03b20e40}
\end{enumerate}

An Ethereum address contains a total of 42 characters including the prefix ``0x", while a Nebulas address contains a total of 50 characters after being added with a checksum composed of 8 characters.

%以太坊地址包括0x前缀共42位字符，星云链地址增加了8位字符的校验码，共50位字符。

\subsection{Extended Address Verification}
In addition to standard address with 50 characters, we also support extended address in order to ensure the security of transfers conducted by users. The traditional bank transfer design is used for reference: In the process of a bank transfer, bank card number of the remittee should be verified, in addition to which the remitter must enter the name of the remittee. The transfer can be correctly processed only when the bank card number and the name match each other. The generating algorithm for extended address is described as follows:

%除了支持50字符的标准地址，为了用户转账的安全，我们还支持扩展地址。借鉴了传统银行转账的设计：转账时除了验证对方的银行卡账号，汇款人还必须输入对方的姓名，只有银行卡账号和姓名都匹配，转账才能正确进行。扩展地址的生成算法如下：

\begin{verbatim}
  Data = sha3_256(Public Key)[-20:]
  CheckSum = sha3_256(Data)[0:4]
  Address = "0x" + Hex(Data + CheckSum)

  ExtData = Utf8Bytes({Nickname or any string})
  ExtHash = sha3_256(Data + ExtData)[0:2]
  ExtAddress = Address + Hex(ExtHash)
\end{verbatim}

An extended address is generated through addition of 2-byte extended verification to the end of a standard address and contains a total of 54 characters. Addition of extended information allows the addition of another element verification to the Nebulas Wallet APP. For example:

%扩展地址在标准地址的尾部追加了2字节的扩展验证，共54位字符。加入扩展信息，使得在星云链钱包应用中可以增加另一个要素验证。例如：
\begin{enumerate}
	\item  The standard address of Alice’s wallet is  0xdf4d22611412132d3e9bd322f82e2940674ec1bc03b20e40, and the extended address after addition of the nickname ``alice" should be \\ 0xdf4d22611412132d3e9bd322f82e2940674ec1bc03b20e40\textbf{e345}.
	\item Alice tells Bob the extended address 0xdf4d22611412132d3e9bd322f82e2940674ec1bc03b20e40e345 and her nickname \textbf{alice}.
	\item Bob enters 0xdf4d22611412132d3e9bd322f82e2940674ec1bc03b20e40e345 and alice in the Wallet App.
	\item The Wallet App verifies the consistency between the wallet address and the nickname in order to avoid the circumstance that Bob enters the account number of another user by mistake.
\end{enumerate}

Both of standard address and extended address can be used for transfer. However, our Nebulas Wallet APP will require extended address mandatorily. Therefore, a user is required to provide nickname of the remittee, based on which the consistency between the nickname and address will be verified in order to further enhance security check.

%标准地址和扩展地址均可以用于转账，我们的星云链钱包应用将会强制使用扩展地址，转账时需要提供对方的昵称，验证地址一致性，进一步加强安全校验。
