\section{Nebulas Force}
\label{sec:nebulasforce}

We use Nebulas Force (NF) to describe the evolutionary capability of the blockchain system and its applications. As the first driving force of the blockchain system and its application development, the Nebulas Force includes three aspects, that is, the Nebulas Virtual Machine (NVM), the upgrade of the core protocol in the blockchain system, and the upgrade of the smart contract running on the blockchain system.

%我们使用星云原力(Nebulas Force, NF)来描述区块链系统及应用的进化能力。星云原力做为驱动区块链系统及应用发展的第一推动力，包括三个方面：星云链虚拟机NVM(Nebulas Virtual Machine)，区块链系统中核心协议的升级，以及运行在区块链系统之上的智能合约的升级。

In Nebulas, we will introduce LLVM to implement the Nebulas Virtual Machine (NVM). The core protocol and the smart contract code will be compiled into NVM bytecode, which is dynamically compiled and optimized with the LLVM just-in-time (JIT) compilation function and eventually executed in the sandbox environment. Meanwhile, with the modular architecture of LLVM, developers can use their familiar programming languages to implement safer and higher-performance smart contracts, providing users with various decentralized applications.

%在星云链中，我们将引入LLVM来实现星云链虚拟机NVM。核心协议和智能合约代码将会编译成NVM字节码，通过LLVM即时编译(Just-in-time compilation)功能，实现其动态编译和优化，最终在沙箱环境中执行。同时借助于LLVM的模块化架构，开发者可以用熟悉的编程语言实现更高性能和更安全的智能合约，给用户带来更丰富的去中心化应用。

For the upgrade of the core protocol in Nebulas, Nebulas will add the core protocol to block structure to carry out the upgrade of the core protocol by supplementing additional data on chains so as to avoid the possible split or bifurcation between developers and communities. With the development of Nebulas communities, the upgrade capability of NF and basic protocols will be gradually open to communities, and communities will define the evolutionary direction of the Nebulas and achieve its upgrade target. With the help of the core technology and the opening concept of NF, Nebulas will have a continuously evolutionary space and an infinitely evolutionary possibility. For example, a series of parameters including the NR algorithm parameter, the PoD incentive amount, the consensus algorithm and the production rate of new tokens can be gradually adjusted during the development of Nebulas without upgrading most client codes.

%对于星云链中的核心协议升级，星云链将核心协议加入到区块中，通过对链上数据的追加实现核心协议的升级，避免开发者和社区的分裂或分叉的可能性。随着星云链社区的发展，NF及基础协议升级能力将逐步开放给社区，由社区定义星云链的进化方向并实现其升级目标。借助于NF这个核心技术和开放性的理念，星云链将会具有持续的进化空间和无限的进化可能。例如，NR算法参数、PoD激励金额、共识算法及新代币的生产速度等一系列参数，都可以在星云链的发展过程中逐渐调整，而不需要大部分客户端代码的升级。

The smart contract is usually considered to be permanent and does not support upgrading. With the help of the design of underlying storage of the smart contract to support the cross-contract visit of state variables, Nebulas can complete the upgrade of the smart contract. This solution is very friendly to developers, making them respond to bugs more rapidly, which can prevent huge losses to users caused by any hacker events.

%智能合约通常被认为是永久性的，不支持升级。星云链通过在智能合约底层存储支持状态变量可跨合约访问的设计，完成智能合约的升级，这种解决方案对开发者友好，使得开发者面对漏洞，能够更快的响应和升级，避免黑客事件给用户带来巨大的损失。

\input{nvm.tex}
\input{block.tex}
\input{smartcontract.tex}
