\section{Nebulas Token NAS}
\label{sec:nascoin}

The Nebulas network has its own built-in token, NAS. NAS plays two roles in the network. First, as the original money in the network, NAS provides asset liquidity among users, and functions as the incentive token for PoD bookkeepers and DIP. Second, NAS will be charged as the calculation fee for running smart contracts. The minimum unit of NAS is $10^{-18}$ NAS.

%星云链网络包含自身的内置货币星云币(NAS)。星云币在网络中体现两个作用：第一，星云币作为网络中的原生货币，提供用户之间的资产流动性，也作为PoD记账人和DIP开发者激励计划的奖励货币；第二，作为运行智能合约的运算费用收取。星云币的最小单位是$10^{-18}NAS$。

Originally, NAS was sold as ERC20 token on the Ethereum platform, with the maximum NAS aggregate of $X = 10^8.$ The issuance modes are as follows:

%星云币最初在以太坊平台上以ERC20代币的方式发售，货币总量最大值为$X=10^8$枚，发行模式如下：
\begin{enumerate}
	\item \textbf{Community Construction:}
	Under the direction of the Nebulas sponsor team, $80\%X$ tokens will be used for Nebulas community construction, including ecological incubation and incentive of the Nebulas community blockchain app (DApp), construction of developer community, business and industrial cooperation, marketing and promotion, academic research, educational investment, laws and regulations, and investment in communities and organizations. Specifically, $5\%X$ will be sold to community impact investors, $5\%X$ as Nebulas community development fund and $70\%X$ for reservation.
	
	%在星云链发起团队主导下，将会有$80\%X$的代币用于星云社区建设，包括星云社社区区块链应用（DApp）生态孵化和激励、开发者社区建设、商业合作和产业合作、市场营销推广、学术研究、教育投资、法律法规、社区及机构投资。其中面向社区影响力投资人售卖$5\%X$，公开ICO售卖$5\%X$，还有$5\%X$作为星云社区发展基金，剩下$65\%X$待做预留。

	\item \textbf{Sponsor and Development Team Incentives:}
	Throughout the development of Nebulas, the sponsor and development teams will continuously make human and material resource contributions in aspects of project organizational structure, technology research and development and ecological operation. As for token allocation, $20\%X$ is reserved for team incentive purpose. This part of NAS is initially locked and will be unlocked one year after the completion of the first NAS sale to the community, and gradually distributed to the sponsor and development teams in three years
	
	%星云链的创始\&开发团队将在星云链的发展过程中，从项目组织架构，技术研发，生态运营上持续做出人力、物力资源的贡献。在代币分配机制上，预留出$20\%X$的部分作为团队激励。这部分星云币初始为锁定状态，自星云币首次面向社区售卖完成一年后开始解除锁定，分三年逐步分发至创始\&开发团队。
\end{enumerate}

After the official launch of Nebulas network, any users with Ethereum ERC20 NAS tokens can claim equivalent NAS of Nebulas network using related credential, and the Ethereum ERC20 NAS tokens will be reclaimed. With the evolution of Nebulas network, NAS will grow in the following way:

%星云链网络正式上线后，所有持有以太坊ERC20 NAS币的用户可以根据凭证，领取星云链网络的等量的星云币，同时以太坊的ERC20 NAS币被回收。随着星云链网络的演化，星云币增长如下：
\begin{enumerate}
	\item \textbf{PoD incentive:} $3\%X$ incentive NAS per year for bookkeepers;
	%每年奖励给记账人的星云币数量为$3\%X$；
	
	\item \textbf{DIP incentive:} $1\%X$ incentive NAS per year for outstanding smart contract developers.
	%每年奖励给优秀智能合约开发者的星云币数量为$1\%X$。
\end{enumerate}